Impact of Context in the Perception of a Robot

### 2015-06-19 main.tex
Large update to the whole article

\rightheader{Impact of Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Impact of Context in the Perception of a Robot}

\author{S\'everin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
Dillenbourg}
\affiliation{CHILI Lab, \'Ecole Polytechnique F\'ed\'erale de Lausanne}

@@

This second point has important implications regarding the design of human-like human-robot
interactions, and we propose to discuss them at the end of the article.
}

\keywords{human-robot interaction, anthropomorphism, cognitive context, eye tracking, gaze patterns}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.). We refer to these characteristics as
the \emph{anthropomorphic design} of the
robot~\citep{fink_anthropomorphism_2012}, and propose that
\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
emerges from the (real or imagined) interaction between a non-human agent (a
robot in our case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the \textbf{dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots}~\citep{lemaignan2014dynamics}, and, even further, we postulate that
anthropomorphism can therefore be considered as a useful \emph{proxy} to these
intricate psychological bonds. This article aims at advancing our understanding
of this phenomenon \textbf{by evidencing the impact of the cognitive
presuppositions implied by the context of the interaction}.

@@

These previous studies investigated users' perception of robots in
different prototyped tasks (routine vs playful, typically boring vs typically
intellectual) and their results nicely supported our general intuition.
In this article, we show that much more subtle variations in the task context do
lead to very noticeable effects as well.

\paragraph{Measuring anthropomorphism} Measuring anthropomorphism raises
interesting methodological challenges, if only because people's perception of
robots change over the duration of their interaction with the
robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
discusses the effects of these changes and differentiates between what she calls
an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation, while a \emph{reflective} perspective would
indicate one's reaction/sense of a situation based on a more in-depth
consideration and contemplation.  In the first phase of interaction with a
non-human agent (a robot in our case), people might respond ``mindlessly''
instead of responding consciously~\citep{nass_machines_2000}, and only after
what is called the \emph{familiarization} period, one might respond in a more
reflective manner instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for instance that subjects interacting
with technologies in ways close to how they would behave towards people, would
deny any human-like interaction in a post-hoc questionnaire, illustrating this
reflective perspective.

Yet, most of the experiments that investigate anthropomorphism in HRI are based
on post-interaction, closed questionnaires or rating scales.  The Godspeed
questionnaire~\citep{bartneck_measurement_2008}, and in particular, its subpart
focused on anthropomorphism, is the main validated questionnaire to assess
anthropomorphism. On 5 point semantic differential scales, people are asked to
rate the following constructs: fake \vs natural, machinelike \vs humanlike,
unconscious \vs conscious, artificial \vs lifelike, moving rigidly \vs moving
elegantly. Because the concept of ``human-likeness'' itself is complex and
abstract, \citet{kahn_jr._robotic_2006} suggest to ask for more concrete
constructs that are typical or unique of the concept of ``human-likeness'', and
\citet{ruijten_introducing_2014} propose for instance a 25-item questionnaire to
measure various concrete aspects of human-likeness. Other
researchers~\citep{zlotowski2014dimensions,salem2015would} also applied a
two-dimensional scale measuring \emph{Human Nature} and \emph{Uniquely Human}
traits of robots, based on an original proposal by \citet{haslam2008attributing}.

@@

\subsection{Hypotheses}

@@

Several hypotheses ensued: \h{1}

There were four hypotheses made in this experiment\fxwarning{need to change
order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4
first, H1 last}. We hypothesized (\textbf{H1}) that the gaze patterns can
distinguish between human and robot interaction scenarios. Further, this gaze
pattern difference can be denoted as the distribution of gaze on areas of
interest in the scene.  Secondly, we hypothesized (\textbf{H2}) that the
difference in gaze patterns between human and robot conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial tendency to anthropomorphize} (\anti), where \anti was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose \anti is low,
the gaze patterns should be significantly different for the robot videos
compared to the human videos.

We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
between high-cognitive and low-cognitive tasks. Finally, we hypothesized
(\textbf{H4}) that the cognitive priming will have an effect on the difference
between \anti and \textit{final tendency to anthropomorphize} (\antf) \ie
\deltaant (where \antf is measured for the post-questionnaire in a similar way
as the \anti).

\fxwarning{This whole para already being discussed under Experimental Design.
Can remove this para}We used stationary eye tracking technique for tracking the
gaze patterns and ``Nao", a robot manufactured by Aldebaran Robotics was used in
this experiment. The interactions were recorded as videos and were then shown to
the participants.  The scenarios that were covered in the videos were aimed at
eliciting the human-like or high-cognitive (HC) feelings for the robot in one
setting and robot-like or low-cognitive (LC) feelings in the other setting. We
tried to keep our distribution of participants uniform across all variations of
the scenarios to avoid any biases to our results. The change in the
feelings\fxwarning{can we have a more specific word than 'feeling'?} of
participants were recorded in the form of response to two questionnaires before
and after the experiment. The difference in the response of the two
questionnaires was used to measure the impact the videos had on the
participants.

\fxwarning{This para is here just to justify why 3rd scenario isn't used. Else
the contents already being discussed in sections 3.1, 3.2}As mentioned earlier,
the human element in the robot interaction was in the form of a command given by
the human to the robot. This command (\eg ``pick up the brown toy") was used to
prime the context thereby classifying the scenario as LC or HC. Initially we had
three different scenarios where the robot/human was asked:

\begin{enumerate}
    \item to pick up a toy
    \item to point to a sound/noise
    \item to show some movements (or dance)
\end{enumerate}

\fxwarning{Is Introduction the best place for justification for not using 3rd
scenario?}Differing from first two scenarios, the third scenario had only one
object in the video \ie~the actor (human or robot). In the first two scenarios,
a participant could make gaze transitions, say, between the robot and the toys
for the first scene. In contrast, in the third scene, a participant could only
look at the robot showing its movements. The third scene, hence, was more
related to observing the various body movements and was not helpful in
identifying differences in gaze patterns based on LC and HC scenarios and
therefore, we did not consider it for our study.

\subsection{Novel Contributions}

The study and results presented in this article lead to two main contributions:
new insights on the impact of the cognitive context of the interaction on the
perception of a robot by humans; a novel unbiased\fxwarning{correct?}
methodology based on eye-tracking to measure anthropomorphic attributions during
a running human-robot interaction.

Our first contribution extends our understanding of the attribution of
human-like characteristics to robot by exploring the role of the interaction
context. As we will show in the article, it appears that \textbf{even relatively
subtle context priming may lead to significantly different anthropomorphic
perceptions of the exact same robot, performing the exact same task}, as
confirmed both by distinct gaze patterns, and different reported perceptions in
questionnaires. As far as we know, this effect had not been previously
evidenced.

Besides, we also introduce a new kind of visual stimuli, specifically designed
to study the impact of non-appearance, non-behavioural related effects on the
human-like perception of robots. We make these video stimuli available to the
community, and therefore invite our colleagues to reproduce our experimental
results.

As a whole, we believe that this article provide a solid contribution, both in
terms of methodology and experimental evidence, to our understanding of one of
the intricate psychological effects that come to play when humans and robots
interact.

@@

This study is build as an eye-tracking experiment (mainly measuring fixation
times on various body parts) where participants watch short videos of an agent
(either a robot or a human) performing very simple task (picking an object or
pointing toward a sound source), in two different socio-cognitive contexts.
These contexts, created by priming and/or audio cues, are designed to elicit
either a shallow cognitive context (that participant would refer as a
\emph{machine-like} situation) or a deeper cognitive context (refered as a
\emph{human-like} situation).

@@

The study follows a 2x2 design, summarized in table~\ref{table:design}. Our two
independent variables are the level of socio-cognitive context (\emph{shallow
cognitive context} vs \emph{deep cognitive context}) and the nature of the
agent appearing in the stimulus (a \emph{robot}, eliciting a \emph{human-robot} interaction
situation, or a \emph{human}, eliciting a \emph{human-human} interaction
situation).

@@

    \caption{\small The study follows a 2$\times$2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive context} vs \emph{deep cognitive context} is between subject.
        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Sound} task,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. While visually identical (see
        screenshots on figure~\ref{fig:stimuli}), the stimuli were introduced
        with different commands in the two conditions \emph{shallow} and
        \emph{deep cognitive
        context}.}

@@

The audio (and audio only) of these four videos was edited to create two sets of
stimuli: one for the \emph{shallow cognitive context} condition, one for the
\emph{deep cognitive context} condition. The audio editing consisted in
inserting \emph{different commands} to initiate the tasks (reported in
table~\ref{table:design}), and, in the \emph{Sound} task, to use as sound source
either a repetitive bip (\emph{shallow cognitive context}) or the sound of a
crying baby (\emph{deep cognitive context}).

@@

    \caption{\small Screenshots of the 2x2 stimuli. Note that the images above have been
    slightly cropped: the original video are framed so that the agent (robot or
    human) always remains entirely visible.}
    \label{fig:stimuli}
\end{figure}

@@

Before starting the experiment, the participants were asked to fill a
questionnaire which had 49 questions. The responses to the questions were scaled
in the 5-point Likert scale, numerically ranging from -2 to 2. The questionnaire
had ten questions from the 10 item big-five personality questionnaire. And then
there were questions taken from Godspeed questionnaire and other
questionnaires. In this report, we refer to this questionnaire as the
pre-questionnaire \ie before the experiment, and it typically took 5 minutes for
participants to fill it.

A second questionnaire was administered at the end of the experiment, that was
almost identical to the pre-questionnaire.  This questionnaire typically took 3
to 4 minutes to fill and we refer to this as the post-questionnaire.

The difference (noted \deltaant, computation detailed below) observed for
each participant between the pre- and post-questionnaires form the dependent
variable of our experiment. It reflects the impact of the video stimuli on the
anthropomorphic perception that they have of robots \emph{in general}: the
Godspeed questions used in the questionnaires are not specific to the Nao robot,
and assess in a broader way how humans perceive robots.

@@

\subsubsection{Participants}

We ran first a pilot study with 10 participants, followed by an experiment with
57 subjects (mean age: 20.9, $SD=3.9$, 32 females and 25 males).

The participants were recruited amongst students of our university. To avoid
students with a high familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted as per the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 57 own a domestic robot (vacuum cleaner).

The study lasted about 15 minutes per participant; each participant was invited
for one session only. Before leaving, each participant was given a reward
equivalent to EUR 10.

The study follows a 2$\times$2 design (table~\ref{table:design}): the
\emph{deep} vs {shallow cognitive context} condition was between-subject ( 31
subjects performed the \emph{deep cognitive} tasks while 26 were in the
\emph{shallow cognitive} condition); the \emph{robot} vs \emph{human} condition
was within-subject (the order of stimuli presentation was counter-balanced over
the 57 participants).

\subsubsection{Pre-questionnaire and familiarization}

\fxwarning{Was it first the pre-questionnaire or the familiarization?}
Before the experiment, participants were made to read, understand and sign a
standard consent form. Participants were then asked to fill the 49 questions of
the pre-questionnaire, without time constraint\fxwarning{right?}.

After the pre questionnaire, we invited the participants to an initial
free interaction with a \textbf{powered-off} Nao robot (we did not constraint
the time, and participants played between 2 and 3 minutes ith the robot).

@@

\subsubsection{Videos}

@@

\subsubsection{Post-questionnaire}

Finally, the participants were asked to fill the post-questionnaire.

@@

Among the two scenarios, the first was one was about the robot/human picking up
a toy and the second one about pointing to the noise. As seen in
figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on the head of
the agent (robot or human), two on the arms (left and right), two on the hands,
two on the legs and one on the torso. Besides, we defined one area of interest
per toy or speaker (depending on the stimulus).

@@

We collected the gazes falling into one of these 10 zones and analyzed
their distribution (producing what we call \emph{gaze patterns}).

@@

An important data to be obtained here is $\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by
taking the difference between the ratio of net dwell time on an AOI and the AOI
fixation coverage summed over all the AOIs in the scene. Hence,
$\delta_{\mathcal{H},\mathcal{R}}$ is expressed as a ratio in the range of 0 to
1. Similarly, the differences between gaze patterns of two participants, where
one watches the LC task, given by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and
the other watches the HC task, given by
$\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.

\subsubsection{Questionnaires processing}

\fxnote{TDB}

@@

Based on the experiments conducted on 57 participants in the human
($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
\emph{deep cognitive context} conditions, we have the following results. (the
detailed statistics and code used for obtaining the results are available here :
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking})

@@

\begin{figure}
    {\includegraphics[width=3.3in]{ManipulationCheck}}
    \caption{Manipulation check}
    \label{fig:ManipulationCheck}
\end{figure}

In our post-questionnaire, we had a question asking the participants about
whether the video has a robot kind of task or a human kind of task on a scale of
-2 to 2 where -2 refers to robot kind of task. As can be seen in figure 2, we
got a significant correlation in this manipulation check ($F[1,36] = 20.42, p <
.01$) which means that the participants that were shown the \emph{shallow
cognitive context} videos identified the task as more robot-like and
participants watching \emph{deep cognitive context} videos perceived the tasks
as more human-like.

\subsection{H1: Gaze differences between human and robot conditions}

We grouped the 8 areas of interest located on the agent into 4 categories : {\sf
head}, {\sf arm} (containing both arms and hands), {\sf torso}, {\sf leg}
(including both legs). And this is the result that we obtained from the ANOVA
between gaze patterns on the AOIs versus the human and robot videos :

@@

{\sf arm}: the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video ($F[1,36] = 18.65, p < .01$)

{\sf leg}: the fixations on the legs were much lower
for the human video as compared to the robot video ($F[1,36] = 2.89, p < .1$)

{\sf torso}: the fixations on the torso was more for the
human video than for the robot video ($F[1,36] = 3.54, p < .1$)

\subsection{H2: Interaction between \anti and gaze patterns}

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the \anti. As can be seen in figure 3(a), there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
p < .01).

\begin{figure}
    \subfigure[Difference in gaze patterns vs \anti]
    {\includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}}
    \subfigure[Gaze patterns for high vs low condition]
    {\includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}}
    \subfigure[Difference between \anti and \antf versus High/Low]
    {\includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}}
    \caption{Hypotheses H2, H3, H4}
\end{figure}

\subsection{H3: Gaze patterns for high vs low cognitive condition}

This test was done only for robot scenario as the human case is
by default a source of HC condition, hence, would not make a big impact in
changing the patterns across the LC and HC conditions. Based on ANOVA results,
taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
both LC and HC conditions, the fixations on the head in the HC condition was
found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
p < .05). For all other AOI groups, the fixations across LC and HC were almost
the same. Figure 3(b) shows the distribution of proportion of time spent gazing
on the 5 AOIs for LC and HC conditions.

\subsection{H4: Difference between \anti and \antf versus High/Low}

ANOVA between \deltaant and the category of cognitive task
\ie HC or LC tells us that \deltaant is greater for HC tasks
than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
figure 3(c).

\section{Discussion}

@@

\section{Conclusion}

>>>>

\rightheader{Impact of Cognitive Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Impact of Context in the Perception of a Robot}

\author{S\'everin Lemaignan, Kshitij Sharma, Ashish Ranjan Jha, Pierre
Dillenbourg}
\affiliation{CHILI Lab, \'Ecole Polytechnique F\'ed\'erale de Lausanne}

@@

}

\keywords{human-robot interaction, anthropomorphism, cognitive context, eye-tracking, gaze patterns}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.).
Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
as the \emph{anthropomorphic design} of the robot, and we call
\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
the (real or imagined) interaction between a non-human agent (a robot in our
case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots~\citep{lemaignan2014dynamics}, and we propose therefore that
anthropomorphism can be a useful \emph{proxy} to these intricate psychological
bonds. This article aims at advancing our understanding of this phenomenon
\textbf{by evidencing the impact of the cognitive presuppositions implied by the
context of the interaction}.

@@

These previous studies investigated users' perception of robots in
prototypical situations (routine \vs playful, typically boring \vs typically
intellectual) and their results nicely supports our general intuition.
In this article, we show that much more subtle variations in the task context do
lead to very noticeable effects as well.

\subsection*{Measuring anthropomorphism}

Measuring anthropomorphism raises
interesting methodological challenges, if only because people's perception of
robots change over the duration of their interaction with the
robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
discusses the effects of these changes and differentiates between what she calls
an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation, while a \emph{reflective} perspective would
indicate one's reaction/sense of a situation based on a more in-depth
consideration and contemplation.  In the first phase of interaction with a
robot, people might respond ``mindlessly'' instead of responding
consciously~\citep{nass_machines_2000}, and only after what is called the
\emph{familiarization} period, one might respond in a more reflective manner
instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for
instance that subjects interacting with technologies in ways close to how they
would behave towards people, would deny any human-like interaction in a post-hoc
questionnaire, illustrating this reflective perspective.

Yet, most of the experiments that investigate anthropomorphism in HRI are based
on post-interaction, closed questionnaires or rating scales.  The Godspeed
questionnaire~\citep{bartneck_measurement_2008}, and in particular, its subpart
focused on anthropomorphism, is the main validated questionnaire to assess
anthropomorphism. On 5-points semantic differential scales, people are asked to
rate the following constructs: fake \vs natural, machinelike \vs humanlike,
unconscious \vs conscious, artificial \vs lifelike, moving rigidly \vs moving
elegantly. Because the concept of ``human-likeness'' itself is complex and
abstract, \citet{kahn_jr._robotic_2006} suggest to ask for more concrete
constructs that are typical or unique of the concept of ``human-likeness'', and
\citet{ruijten_introducing_2014} propose for instance a 25-item questionnaire to
measure various concrete aspects of human-likeness. Other
researchers~\citep{zlotowski2014dimensions,salem2015would} also applied a
two-dimensional scale measuring \emph{Human Nature} and \emph{Uniquely Human}
traits of robots, based on an original proposal by \citet{haslam2008attributing}.

@@

\subsection*{Hypotheses}

@@

Several hypotheses ensued, our baseline hypothesis \h{0} being that \emph{shallow
cognitive contexts} and \emph{deep cognitive contexts} are recognized
(manipulation check) and interpreted by the participants as being respectively
\emph{machine-like} (low level of anthropomorphic attributions) or
\emph{human-like} (higher level of anthropomorphic attributions).

Our first hypothesis \h{1} is then that gaze behaviour only is sufficient to
know if a subject is looking at a robot or at a human.  More precisely, we
hypothesize that the distribution of gaze fixations on the different body parts
is significantly different when watching a robot or a human performing the same
task.

Secondly, we hypothesize (\h{2}) that the \emph{difference} of gaze
behaviours between the human and robot conditions correlates with the
participants' initial tendency to anthropomorphize, measured from a standard
pre-questionnaire: we expect that people with high tendency to anthropomorphize
will tend to have similar gaze behaviours while watching either a robot or a
human performing the same task.

Then, we hypothesize (\h{3}) that the gaze fixations on the head are significantly
different depending on the cognitive context, and that a deeper cognitive
context corresponds to longer gaze fixations on the head. This would in turn
interpreted at \emph{gaze fixations on the head is a proxy for an higher
level of human-likeness attribution}, the core hypothesis of this article.

Finally, the hypothesis \h{4} examines whether the cognitive context affects the
general tendency to anthropomorphize, \ie whether observing a
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots (and vice versa).

@@

As hinted, this study is build as an eye-tracking experiment (using a stationary
eye-tracker) where participants watch short videos of an agent -- either a robot
(Aldebaran Robotics' Nao) or a human -- performing very simple task (picking an
object or pointing toward a sound source), in two different socio-cognitive
contexts.  These contexts, created by priming and/or audio cues, are designed to
elicit either a shallow cognitive context (that participant would refer as a
\emph{machine-like situation}) or a deeper cognitive context (refered as a
\emph{human-like situation}).

Besides eye-tracking, the participants' perception of robots is assessed through a
pre- and a post-questionnaire, described below.

@@

The study follows a 2$\times$2 design, summarized in table~\ref{table:design}. Our two
independent variables are the level of socio-cognitive context (\emph{shallow
cognitive context} \vs \emph{deep cognitive context}) and the nature of the
agent appearing in the stimulus (a \emph{robot}, eliciting a \emph{human-robot} interaction
situation, or a \emph{human}, eliciting a \emph{human-human} interaction
situation).

@@

    \caption{\small The study follows a 2$\times$2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive context} \vs \emph{deep cognitive context} is between subject.
        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Sound} task,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. Figure~\ref{fig:stimuli} shows
        pictures of the four stimuli.}

@@

The audio (and audio only) of these four videos was then edited to create two
sets of stimuli: one for the \emph{shallow cognitive context} condition, one for
the \emph{deep cognitive context} condition. The audio editing consisted in
inserting different commands to initiate the tasks (reported in
table~\ref{table:design}): in the \emph{Picking} task for instance, the object
that the agent had to pick was described either as a \emph{``brown toy''} or as
\emph{``your favorite toy''}. In the former case, the object was refered through
visible, objective features which do not suppose as deep cognitive capabilities
as in the latter case where the agent is implicitly supposed to have
tastes and preferences such as it can choose a toy as its favorite.

This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
toy''}) set the cognitive context (\emph{shallow} \vs \emph{deep}) and was
expected to lead to different perceptions of the interaction
(\emph{machine-like} \vs \emph{human-like}). We reinforced this effect in the
\emph{Sound} task: not only the verbal priming but also the sound played by the
speakers during the task was altered: either a repetitive bip (\emph{shallow
cognitive context}) or the sound of a crying baby (\emph{deeper cognitive
context}).

@@

    \caption{\small Screenshots of the 2$\times$2 stimuli. Note that the images above have been
    slightly cropped: the original video are framed so that the agent (robot or
    human) always remains entirely visible.}
    \label{fig:stimuli}
\end{figure}

Section~\ref{stimuli_design}, at the end of the article, specifically discusses
the design constraints that were accounted for while creating the above stimuli.

@@

Before starting the experiment, the participants were asked to fill a
pre-questionnaire which had 49 questions (5-point Likert scale). The
questionnaire comprised of questions assessing their familiarity for robots, 10
items from \emph{big-five} personality questionnaire, 15 questions taken from
Godspeed questionnaire (questions related to \emph{anthropomorphism},
\emph{likeability} and \emph{perceived intelligence}), 20 questions rating
human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
the pre- and post-questionnaires are available online:
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
typically took 5 minutes for participants to fill. The results were turned into
a score noted \anti (\emph{initial tendency to anthropomorphize}) following a
method presented below (section~\ref{questionnaires_processing}).

The post-questionnaire was administered at the end of the experiment, and was
close to the pre-questionnaire: the personality questions were omitted, and a
manipulation check question was added (\emph{``In your opinion, the tasks that
you watched were more: A robot kind of task ... A human kind of task''}).
This questionnaire typically took 3 to 4 minutes to fill. The resulting score is
noted \antf (\emph{final tendency to anthropomorphism}).

The difference \deltaant measured for each participant between the pre-
and post-questionnaires forms the dependent variable of our experiment. It
reflects the impact of the video stimuli on the anthropomorphic perception that
they have of robots \emph{in general}: the Godspeed questions used in the
questionnaires are not specific to the Nao robot used in this particular
experiment, and indeed assess how humans perceive robots in a broad sense.

@@

\paragraph{Participants}

We ran first a pilot study with 10 participants, followed by an experiment with
57 subjects (mean age: 20.9, $SD=3.9$, 32 females and 25 males).
The participants were recruited amongst students of our university. To avoid
students with a high familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 57 owned a domestic robot (vacuum cleaner).

The study lasted about 15 minutes per participant; each participant was invited
for one session only.

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
condition was between-subject ( 31 subjects performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the 57 participants).

\paragraph{Pre-questionnaire and familiarization}

\fxwarning{Was it first the pre-questionnaire or the familiarization?}
Before the experiment, participants were made to read, understand and sign a
consent form. Participants were then asked to fill the 49 questions of
the pre-questionnaire, without time constraint\fxwarning{right?}.

After the pre-questionnaire, we invited the participants to an initial
free interaction with a \textbf{powered-off} Nao robot (we did not constraint
the time, and participants played between 2 and 3 minutes with the robot).

@@

\paragraph{Videos}

@@

\paragraph{Post-questionnaire}

Finally, the participants were asked to fill the post-questionnaire.
Before leaving, each participant was given a reward
equivalent to EUR 10.

@@

As seen in figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on
the head of the agent (robot or human), two on the arms (left and right), two on
the hands, two on the legs and one on the torso. Besides, we defined one area of
interest per toy or speaker (depending on the stimulus).

@@

We collected the gazes falling into one of these 10 zones and normalized them to
account for different total video duration and surface of AOIs between the robot
and human conditions\fxfatal{do we?}. We finally analyzed their distribution,
producing what we call \emph{gaze patterns}.

@@

\fxfatal{To be rewritten} An important data to be obtained here is
$\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by taking the difference
between the ratio of net dwell time on an AOI and the AOI fixation coverage
summed over all the AOIs in the scene. Hence, $\delta_{\mathcal{H},\mathcal{R}}$
is expressed as a ratio in the range of 0 to 1. Similarly, the differences
between gaze patterns of two participants, where one watches the LC task, given
by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and the other watches the HC
task, given by $\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze
variables.

\subsubsection{Questionnaires processing}
\label{questionnaires_processing}
\fxnote{TDB}

@@

Based on the experiments conducted on 57 participants in the human
($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
\emph{deep cognitive context} conditions, we have the following
results.\footnote{The
detailed statistics and code used for obtaining the results are available here :
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{ManipulationCheck}
    \caption{\fxfatal{Incorrect nb of particpants! Label should be shallow/deep
    instead of low/high}Manipulation check}
    \label{fig:ManipulationCheck}
\end{figure}

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F[1,36] = 20.42, p < .01$) which validates our manipulation
and supports \h{0}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

\subsection{Gaze differences between human and robot conditions}

We grouped the 8 areas of interest located on the agent into 4 categories : {\sf
head}, {\sf arms} (containing both arms and hands), {\sf torso}, {\sf legs}
(including both legs). Running an ANOVA against gaze fixations on the areas of
interest and the robot \vs human conditions, we obtain the following results:

@@

{\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video ($F[1,36] = 18.65, p < .01$)

{\sf legs}: the fixations on the legs were much lower
for the human video as compared to the robot video ($F[1,36] = 2.89, p < .1$)

{\sf torso}: the fixations on the torso were higher for the
human video than for the robot video ($F[1,36] = 3.54, p < .1$)

In summary, and over the duration of these shorts videos, the gaze behaviours
were significantly different between the robot and human conditions, supporting
\h{1}.

\subsection{Impact of the tendency to anthropomorphize on the robot \vs human
gazing behaviours}

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the \anti. As can be seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
$p < .01$).

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}
    \caption{Difference in gaze patterns \vs \anti}
    \label{h2}
\end{figure}

\subsection{Gaze behaviours in shallow \vs deep cognitive contexts}

We analysed these possible correlations for robot condition only: the human case is
inherently a source of deep cognitive context, hiding the effects of our
manipulation on a shallow \vs deep cognitive context.

Based on ANOVA results, taking the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf
hands}, {\sf torso}, {\sf legs} for the robot in both the shallow and deep
cognitive context conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F[1,36] = 4.55, p < .05$). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOIs for the two
conditions.

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}
    \caption{Gaze fixations on the different areas on interest, for shallow \vs
    deep cognitive context conditions.}
    \label{h3}
\end{figure}

This constitutes the main result of this study: inducing a deeper cognitive
context for the same interaction suffices to lead to significantly longer
fixations on the agent's head.

\subsection{Correlation between cognitive context and changes in anthropomorphic
attributions}

Running an ANOVA against the evolution of anthropomorphic attributions
(\deltaant) over the duration of the experiment, in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F[1,36] = 6.54, p < .05$,
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, subjects primed with a deeper cognitive context report
a significantly higher tendency to anthropomorphize robots \emph{in general} (as
the questionnaires on anthropomorphic attributions explicitely refered to
\emph{robots in general}).

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
    \caption{Difference between \anti and \antf in the shallow and deep
    cognitive contexts.}
    \label{h4}
\end{figure}

This result supports \h{4} and validate that the cognitive context impacts the
attribution of anthropomorphic features to robots. This, in turn, supports
the \emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for
higher levels of human-likeness attributions}.

\section{Discussion and Conclusion}

\subsection{Discussion}

@@

\subsection{Summary and Contributions}

The study and results presented in this article lead to two main contributions:
new insights on the impact of the cognitive context of the interaction on the
perception of a robot by humans; a novel unbiased methodology based on
eye-tracking to measure anthropomorphic attributions during a running
human-robot interaction.

Our first contribution extends our understanding of the attribution of
human-like characteristics to robot by exploring the role of the interaction
context. As we show in the article, it appears that \textbf{even relatively
subtle context priming may lead to significantly different anthropomorphic
perceptions of the exact same robot, performing the exact same task}, as
confirmed both by distinct gaze patterns, and different reported perceptions in
questionnaires. As far as we know, this effect had not been previously
evidenced.
